---
title: "Lab 10"
author: "Lucas Boyd"
date: "11/29/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# attach packages
library(beepr)
library(praise)
library(cowsay)
library(sf)
library(paletteer)
library(here)
library(tidyverse)
library(janitor)
```

## beepr::beep()

```{r}
beep() # this shit beeps!!!!!
beep(8) # biiiiiiiig fun
```
Use beep() to give an audio alert
```{r, eval = FALSE} 
# for loop + beep

for (i in rev(seq(1:99))) {
  print(paste(i, "bottles of beer on the wall"))}

beep(4)
```
rev() function reverses the sequence seq()
paste() paste things together to create a new string
eval = FALSE so it is not evaluated when knitting

## praise is nice 

```{r}
praise("${EXCLAMATION}!!! This code works ${adverb_manner}!")
```

## cowsay::say()

```{r}
say(what = "go off", by = "hypnotoad", )
```

## usethis()
usethis::edit_r_profile in the console to edit your r profile (this changes things across all projects)

R project first, then GitHub and repo
usethis::use git() - then click yes twice
usethis::use github() - one more yes
this will take you to github with a fresh new repo
if you rename the branch, copy the code to clipboard and run it in the TERMINAL

## paletteer: aggregated color palettes

run > View(palettes_d_names) in the console to check them out

```{r}
storms %>% 
  group_by(name) %>% 
  summarize(min_pressure = min(pressure, na.rm = TRUE)) %>% 
  slice_min(n = 10, min_pressure) %>% # the lowest 10 min pressures
  ggplot(aes(x = min_pressure, y = name)) +
  geom_col(aes(fill = name)) +
  scale_fill_paletteer_d("palettetown::vulpix") # _d for discrete and _c for continuous
```

## Map of Jornada LTER Vegetation

sf or simple features makes important info stick together
```{r}
jornada_veg <- read_sf(here("data", "doc.kml")) %>% 
  select(Name) %>% 
  clean_names()

ggplot() + 
  geom_sf(data = jornada_veg, aes(fill = name)) +
  scale_fill_paletteer_d("palettetown::beedrill") +
  theme_minimal()

# update this map so that 
# each vegetation type has a different fill color
# update theme
# customize the color palette

ggsave(filename = "sick_graph.png", width = 8, height = 5)
```




